---
output:
  knitrBootstrap::bootstrap_document:
    theme.chooser: TRUE
    highlight.chooser: TRUE
---

<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Cars example}
-->

# Cars example #
From [statmethods.net](http://www.statmethods.net/advgraphs/ggplot2.html).

```{r cars_setup}
# ggplot2 examples
library(ggplot2)
#use color brewer as default discrete colors
scale_colour_discrete <- function(...) scale_color_brewer(palette="Set1", ...)
scale_fill_discrete <- function(...) scale_fill_brewer(palette="Set1", ...)

data('mtcars')
# create factors with value labels
mtcars$gear <- factor(mtcars$gear,levels=c(3,4,5),
     labels=c("3gears","4gears","5gears"))
mtcars$am <- factor(mtcars$am,levels=c(0,1),
     labels=c("Automatic","Manual"))
mtcars$cyl <- factor(mtcars$cyl,levels=c(4,6,8),
   labels=c("4cyl","6cyl","8cyl"))
head(mtcars)
```
##  Kernel density plots for mpg ##
Grouped by number of gears (indicated by color).
```{r cars_density, dev='png', warning=FALSE}
qplot(mpg, data=mtcars, geom="density", fill=gear, alpha=I(.5),
   main="Distribution of Gas Milage", xlab="Miles Per Gallon",
   ylab="Density")
```
## Scatterplot of mpg vs. hp ##
For each combination of gears and cylinders in each facet, transmission type is represented by shape and color.
```{r cars_scatter, dev='png', warning=FALSE}
qplot(hp, mpg, data=mtcars, shape=am, color=am,
   facets=gear~cyl, size=I(3),
   xlab="Horsepower", ylab="Miles per Gallon")
```

## Regressions of mpg on weight ##
Separate for each number of cylinders.
```{r cars_regressions, dev='png', warning=FALSE}
ggplot(data = mtcars, aes(x = wt, y = mpg, color = cyl)) +
  geom_point() + geom_smooth(method = "lm") +
   labs(title = "Regression of MPG on Weight", x = "Weight", y = "Miles per Gallon")
```

## Boxplots of mpg by number of gears ##
Observations (points) are overlayed and jittered.
```{r cars_boxplots, dev='png', warning=FALSE}
qplot(gear, mpg, data=mtcars, geom=c("boxplot", "jitter"),
   fill=gear, main="Mileage by Gear Number",
   xlab="", ylab="Miles per Gallon")
```

Author: [Jim Hester](http://jimhester.com)
Created: 2013 Mar 20 10:57:07 AM
Last Modified: 2016 Feb 23 09:38:05 AM
