```{r include=FALSE}
render_html()
```
# Cars example #
from [statmethods.net](http://www.statmethods.net/advgraphs/ggplot2.html)

```{r cars_setup}
render_html()
# ggplot2 examples
library(ggplot2)
rm(mtcars)
#use color brewer as default discrete colors
scale_colour_discrete <- function(...) scale_color_brewer(palette="Set1", ...)
scale_fill_discrete <- function(...) scale_fill_brewer(palette="Set1", ...)

# create factors with value labels
mtcars$gear <- factor(mtcars$gear,levels=c(3,4,5),
     labels=c("3gears","4gears","5gears"))
mtcars$am <- factor(mtcars$am,levels=c(0,1),
     labels=c("Automatic","Manual"))
mtcars$cyl <- factor(mtcars$cyl,levels=c(4,6,8),
   labels=c("4cyl","6cyl","8cyl"))
```
##  Kernel density plots for mpg ##
grouped by number of gears (indicated by color)
```{r cars_density, dev='png', warning=FALSE}
qplot(mpg, data=mtcars, geom="density", fill=gear, alpha=I(.5),
   main="Distribution of Gas Milage", xlab="Miles Per Gallon",
   ylab="Density")
```
## Scatterplot of mpg vs. hp ##
for each combination of gears and cylinders in each facet, transmission type is represented by shape and color
```{r cars_scatter, dev='png', warning=FALSE}
qplot(hp, mpg, data=mtcars, shape=am, color=am,
   facets=gear~cyl, size=I(3),
   xlab="Horsepower", ylab="Miles per Gallon")
```

## Regressions of mpg on weight ##
Seperate for each number of cylinders
```{r cars_regressions, dev='png', warning=FALSE}
qplot(wt, mpg, data=mtcars, geom=c("point", "smooth"),
   method="lm", formula=y~x, color=cyl,
   main="Regression of MPG on Weight",
   xlab="Weight", ylab="Miles per Gallon")
```

## Boxplots of mpg by number of gears ##
observations (points) are overlayed and jittered
```{r cars_boxplots, dev='png', warning=FALSE}
qplot(gear, mpg, data=mtcars, geom=c("boxplot", "jitter"),
   fill=gear, main="Mileage by Gear Number",
   xlab="", ylab="Miles per Gallon")
```

Author: [Jim Hester](http://jimhester.com)
Created: 2013 Mar 20 10:57:07 AM
Last Modified: 2013 Apr 23 02:23:28 PM
