```{r include=FALSE}
render_html()
```
# 2d graphs #
These 2d examples are both from Winsong Chang's excellent [R Graphics Cookbook](http://www.amazon.com/R-Graphics-Cookbook-Winston-Chang/dp/1449316956)
## Correlation Matrix Example ##
### Correlation plot ###
```{r 2d_3d_plot, dev='png', warning=FALSE}
library(corrplot)
corrplot(mcor)
```
### Regular R output ###
```{r 2d_3d_data}
#for the dataset
library(ggplot2)
rm(mtcars)
mcor <-cor(mtcars)
# Print mcor and round to 2 digits
round(mcor,digits=2)
```
### HTML table using xtable ###
```{r 2d_3d_xtable, results='asis'}
library(xtable)
print(xtable(mcor), type='html')
```
## Network Graph Example ##
```{r 2d_3d_network_data, dev='png'}
library(igraph)
# Specify edges for a directed graph
gd <-graph(c(1,2, 2,3, 2,4, 1,4, 5,5, 3,6))
plot(gd)
# For an undirected graph
gu <-graph(c(1,2, 2,3, 2,4, 1,4, 5,5, 3,6),directed=FALSE)
# No labels
plot(gu,vertex.label=NA)
```
# 3d graphs #
This example is from [Yihui's response](http://stackoverflow.com/questions/14879210/including-a-interactive-3d-figure-with-knitr) to a stack overflow question.

Need to load the CanvasMatrix library and the hook_webgl code to get 3d graphs to work
```{r setup}
has_X11 = Sys.getenv('DISPLAY') != ""
if(has_X11)
  knit_hooks$set(webgl = hook_webgl)
```
```{html}
<script src="https://dl.dropbox.com/u/15335397/misc/CanvasMatrix.js"></script>
```
<script src="https://dl.dropbox.com/u/15335397/misc/CanvasMatrix.js"></script>

## point 3d graph ##
```{r 2d_3d_points, webgl=TRUE, eval=has_X11}
library(rgl)
x <- sort(rnorm(1000))
y <- rnorm(1000)
z <- rnorm(1000) + atan2(x, y)
  plot3d(x, y, z, col = rainbow(1000))
```
## spheres 3d graph ##
```{r 2d_3d_spheres, webgl=TRUE, eval=has_X11}
open3d()
spheres3d(x, y, z, col = rainbow(1000))
```

Author: [Jim Hester](http://jimhester.com)
Created: 2013 Mar 27 10:54:38 PM
Last Modified: 2013 Apr 23 02:24:13 PM
